Rule Synthesis for Network Intrusion Detectors

### 2020-06-04 paper/paper.tex
fix score formula IV.C5

\subsubsection{Weight Optimization}
\label{sec:weight-optimization}
Obtaining the best possible ranking for the golden rule boils down to 
finding optimal weights for the heuristic functions. The sum of rankings 
of the golden rules, for a set of $N$ attacks, is given by 
$R(W) = \sum_{i=1}^{N}\mathit{R_i}$, where $R_i$ is the ranking based on 
the score provided by 
$(w_1 + popt) \cdot (w_2 + ncont) \cdot (w_3 + pcont) \cdot (w_4 + phttp)$ 
and $W = \langle{}w_1, w_2, w_3, w_4\rangle{}$ are the weights considered 
for each heuristic.
%
We resorted to the Differential Evolution algorithm from SciPy\cite{diff-evo-scipy}
to compute the optimal weights. The optmization consists in minimizing the function 
of every attack's golden rule ranking in our set given a combination of weights. 
Formally, $W  = \displaystyle \argmin_W R(W)$.
%
The algorithm also takes as input the range of the weights (between 0 and 1) 
and the max number of generations, which we set to 10 (confirmation whether 
this number suffices remains to future work). The weights are 
as follows $\langle{}0.280, 0.057, 0.043, 0.490\rangle{}$.

>>>>

\subsubsection{Weight Optimization}
\label{sec:weight-optimization}
Obtaining the best possible ranking for the golden rule boils down to 
finding optimal weights for the heuristic functions. The sum of rankings 
of the golden rules, for a set of $N$ attacks, is given by 
$R(W) = \sum_{i=1}^{N}\mathit{R_i}$, where $R_i$ is the ranking based on 
the score provided by 
$[(w_1 \cdot popt) + (w_2 \cdot ncont) + (w_3 \cdot pcont) + (w_4 \cdot phttp)]/4$ 
and $W = \langle{}w_1, w_2, w_3, w_4\rangle{}$ are the weights considered 
for each heuristic.
%
We resorted to the Differential Evolution algorithm from SciPy\cite{diff-evo-scipy}
to compute the optimal weights. The optmization consists in minimizing the function 
of every attack's golden rule ranking in our set given a combination of weights. 
Formally, $W  = \displaystyle \argmin_W R(W)$.
%
The algorithm also takes as input the range of the weights (between 0 and 1) 
and the max number of generations, which we set to 10 (confirmation whether 
this number suffices remains to future work). The weights are 
as follows $\langle{}0.280, 0.057, 0.043, 0.490\rangle{}$.
